A new simplified manual tour, with application to exploring classification boundaries in high dimensions

### 2022-07-07 paper/paper.Rmd
penguins colour matching

>>>>

To illustrate the usefulness of the manual tour use the penguins data [@penguins]. We will show how classification boundaries can be explored and better understood using a manual tour, on projections and slices through 4D space.

```{r penguins-scatmat, out.width="100%", width=10, height=10, fig.cap="Scatterplot matrix of the (standardised) penguins data."}
library(tidyverse)
library(palmerpenguins)
library(GGally)
penguins_data <- penguins[, c(1,3, 4, 5, 6)] %>%
  drop_na() %>%
  mutate(across(where(is.numeric), function(x) (x-mean(x))/sd(x)))
ggscatmat(penguins_data, columns = 2:5, col="species") +
  scale_colour_manual("", values=c("Adelie" = "#5E82B6", "Chinstrap" = "#E19C24", "Gentoo" = "#8FB132")) +
  theme(legend.position = "bottom")
```

### 2022-07-07 paper/paper.tex
penguins colour matching

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figure-latex/penguins-scatmat-1} \caption{Scatterplot matrix of the penguins data.}\label{fig:penguins-scatmat}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=1\linewidth]{paper_files/figure-latex/penguins-scatmat-1} \caption{Scatterplot matrix of the (standardised) penguins data.}\label{fig:penguins-scatmat}
\end{figure}
